HSC Synthetic Pipeline I: Basic Design and Characterization of HSC Photometric Performance

### 2017-04-19 draft/ms_v3.tex
Start the final edits

% Version 0; Only rough outline by SH
% Version 1; First draft by SH
% Version 2; Main text is finished; with edits from Susan Foster

@@

% Package Settings
%\usepackage{hyperref}
%\hypersetup{colorlinks=true,
%            citecolor=cyan,
%            linkcolor=cyan,
%            filecolor=magenta,
%            urlcolor=cyan}
%\urlstyle{same}
%% ------------------------------------------------------------------------------------ %%

@@

\altaffiltext{1}{Kavli Institute for the Physics and Mathematics of the
    Universe, The University of Tokyo Institutes for Advanced Study,
    the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan}
\altaffiltext{2}{Department of Astronomy and Astrophysics, University of California,
    Santa Cruz, 1156 High Street, Santa Cruz, CA 95064 USA}
\altaffiltext{3}{Department of Astrophysical Sciences, Princeton University,
    4 Ivy Lane, Princeton, NJ 08544}
\altaffiltext{4}{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
\altaffiltext{5}{McWilliams Center for Cosmology, Department of Physics,
    Carnegie Mellon University, Pittsburgh, PA 15213, USA}
\altaffiltext{6}{SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
    Tokyo, 181--8588, Japan}
\altaffiltext{7}{Other affiliations}

@@

    As the last step, \synpipe{} matches the input catalog to the results within a
    radius that is specified by the user, and merges all the \unforced{} and
    \forced{} measurements from all the \texttt{Patches}.
    Each unmatched object from the input catalog is also passed to the results catalog 
    with a unique label.
    In the case of multiple matches, the user can choose between returning only the 
    closest match or returning all objects within the matching radius (the nearest one 
    is labeled as such).

    \song{Susan's edit ends here; and Song has went through the previous sections.}
    \susan{Susan made some minor additional edits to the preceding text on 4/17/2017.}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %%
\susan{Susan started editing here on 4/17/2017.}
\section{Generation of Synthetic Dataset}
    \label{sec:test}

@@

        \item Can represent both good and bad seeing conditions in the current $i$-band
            data of the HSC survey.
              \end{enumerate}
              In addition to satisfying these criteria, the selected \tracts {}  show the photometric uncertainties under both good and bad seeing conditions, since for any given star or galaxy, different seeing conditions affect its
            central S/N on the \coadd{} images and, therefore, also impact the
            detection and deblending processes in \hscpipe{}.

@@

For star selection, we use the sample from \citet{Leauthaud2007}. 
     We use not only the \texttt{SExtractor} stellar classification index (\texttt{CLASS\_STAR}) but also the peak surface brightness above background (\texttt{MU\_MAX}) and
    half-light radius (\texttt{RHL}) to select stars with clean photometry. 
    The classification is reliable down to $I_{\mathrm{F814W}}{\sim}25.2$ mag.
    We match this sample of stars with the HSC UltraDeep--COSMOS data that currently
    reach to about ${\sim}27.2$ mag in $i$-band.
    After filtering the matched sample through basic quality cuts (see \ref{app:qc}),
    we gather five-band HSC photometry for 14,472 stars.
    To get a larger sample for the test, we resample the five-band magnitude
    distributions using \texttt{astroML} (\citealt{astroml}) alternative
    implementation of the \texttt{extreme-deconvolution} algorithm developed by
    \citet{Bovy2011}
    \footnote{\texttt{https://github.com/jobovy/extreme-deconvolution/}} to
    generate 100,000 synthetic stars.
    In Fig \ref{fig:star_sample}, we show that the magnitude and color distributions of
    the real COSMOS stars are nicely recovered by the resampled stars in all
   five-band magnitude and two color-color space distributions. \susan{Later you use "2-D color-color" Should it also be 2-D here?}

>>>>

% Version 0; Rough outline by SH
% Version 1; First draft by SH
% Version 2; Finish main text; with edits from Susan Foster
% Version 3; More edits from Susan

@@

@@

\altaffiltext{1}{Kavli Institute for the Physics and Mathematics of the
    Universe, The University of Tokyo Institutes for Advanced Study,
    the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan}

\altaffiltext{2}{Department of Astronomy and Astrophysics, University of California,
    Santa Cruz, 1156 High Street, Santa Cruz, CA 95064 USA}

\altaffiltext{3}{Department of Astrophysical Sciences, Princeton University,
    4 Ivy Lane, Princeton, NJ 08544}

\altaffiltext{4}{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}

\altaffiltext{5}{McWilliams Center for Cosmology, Department of Physics,
    Carnegie Mellon University, Pittsburgh, PA 15213, USA}

\altaffiltext{6}{SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
    Tokyo, 181--8588, Japan}

\altaffiltext{7}{Other affiliations}

@@

    As the last step, \synpipe{} matches the input catalog to the results within a
    radius that is specified by the user, and merges all the \unforced{} and
    \forced{} measurements from all the \texttt{Patches}.
    Each unmatched object from the input catalog is also passed to the results catalog
    with a unique label.
    In the case of multiple matches, the user can choose between returning only the
    closest match or returning all objects within the matching radius (the nearest one
    is labeled as such).
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %%
\section{Generation of Synthetic Dataset}
    \label{sec:test}

@@

        \item Can represent both good and bad seeing conditions in the current $i$-band
            data of the HSC survey.
            Since for any given star or galaxy, different seeing conditions affect its
            central S/N on the \coadd{} images and, therefore, also impact the
            detection and deblending processes in \hscpipe{}.

@@

    \song{Song Huang's edit}
    For star selection, we use the sample from \citet{Leauthaud2007}.
    We use not only the \texttt{SExtractor} stellar classification index
    (\texttt{CLASS\_STAR}) but also the peak surface brightness above background
    (\texttt{MU\_MAX}) and half-light radius (\texttt{RHL}) to select stars with clean
    photometry.
    The classification is reliable down to $I_{\mathrm{F814W}}{\sim}25.2$ mag.
    We match this sample of stars with the HSC UltraDeep--COSMOS data that currently
    reach to about ${\sim}27.2$ mag in $i$-band.
    After filtering the matched sample through basic quality cuts (see \ref{app:qc}),
    we gather five-band HSC photometry for 14,472 stars.
    To get a larger sample for the test, we resample the five-band magnitude
    distributions using \texttt{astroML} (\citealt{astroml}) alternative
    implementation of the \texttt{extreme-deconvolution} algorithm developed by
    \citet{Bovy2011}
    \footnote{\texttt{https://github.com/jobovy/extreme-deconvolution/}} to
    generate 100,000 synthetic stars.
    In Fig \ref{fig:star_sample}, we show that the magnitude and color distributions of
    the real COSMOS stars are nicely recovered by the resampled stars in all
    five-band magnitude and two color-color space distributions.
